RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-15 paper/two_pager.tex
Add parentheses

\begin{enumerate}
\item We read a frame of video and convert it to HSV space
\item Perform a slew of static transforms to try and determine,
      based on the content of a single frame, which areas are and
      are not water/sky/land/objects (see Figure \ref{fig:boatconf}:
  \begin{enumerate}
    \item Use a 2-class k-means classification to
          identify non-water based areas
    \item Suppress wave reflections using squared cluster distance as confidence
    \item Use Matlab's \texttt{bwareaopen} to
          identify and suppress the connected areas of the sky
  \end{enumerate}
\item Use optical flow information from a given pair of frames to
      locate the moving objects in a frame, based on Matlab's
      \texttt{opticalFlowFarneback}, and a simple model of the
      expected flow of the water to filter out the background in
      the optical flow space, resulting in confidence scores
      as in Figure \ref{fig:diff_magnitude}
\item Combine the above to determine a set of viable blobs using erodes/dilates
      and Matlab's \texttt{bwlabel}
\item Associate the blobs with each other and with preexisting objects,
      creating new objects for blobs that can't be associated with any
      preexisting objects, based on:
  \begin{enumerate}
    \item Similarity in blob/object velocities
    \item Similarity of blob/object position
    \item Taking weighted averages of velocities to combine them, and
          combining the object bounding boxes
  \end{enumerate}
\item Update objects in preparation for the next frame, updating
      positions using velocities, reducing and increasing confidence
      scores as appropriate, deleting objects with sufficiently low
      scores
\end{enumerate}

>>>>

\begin{enumerate}
\item We read a frame of video and convert it to HSV space
\item Perform a slew of static transforms to try and determine,
      based on the content of a single frame, which areas are and
      are not water/sky/land/objects (see Figure \ref{fig:boatconf}):
  \begin{enumerate}
    \item Use a 2-class k-means classification to
          identify non-water based areas
    \item Suppress wave reflections using squared cluster distance as confidence
    \item Use Matlab's \texttt{bwareaopen} to
          identify and suppress the connected areas of the sky
  \end{enumerate}
\item Use optical flow information from a given pair of frames to
      locate the moving objects in a frame, based on Matlab's
      \texttt{opticalFlowFarneback}, and a simple model of the
      expected flow of the water to filter out the background in
      the optical flow space, resulting in confidence scores
      as in Figure \ref{fig:diff_magnitude}
\item Combine the above to determine a set of viable blobs using erodes/dilates
      and Matlab's \texttt{bwlabel}
\item Associate the blobs with each other and with preexisting objects,
      creating new objects for blobs that can't be associated with any
      preexisting objects, based on:
  \begin{enumerate}
    \item Similarity in blob/object velocities
    \item Similarity of blob/object position
    \item Taking weighted averages of velocities to combine them, and
          combining the object bounding boxes
  \end{enumerate}
\item Update objects in preparation for the next frame, updating
      positions using velocities, reducing and increasing confidence
      scores as appropriate, deleting objects with sufficiently low
      scores
\end{enumerate}
